Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
fix citations on both pdf and html

Unlike text-based commands which are only valid once complete (e.g
\texttt{SELECT\ *\ FRO} versus \texttt{SELECT\ *\ FROM\ user\_table}),
the target of demonstration commands (the value of a DOM element under
the cursor) is the same during both hover and click (incomplete command
versus complete command). This allows us to take a small step further by
executing a command before a user completes it, thereby providing them
with a preview of the results on hover.

@@

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. Because demonstrations can span
across several websites and involve complex data access automation
tasks, its interface does not provide \emph{full} live feedback about
its generalizations or the values to be scrapped until all the
demonstrations have been provided and the generated program has been
run. If run on a website it has encountered before, Rousillon makes all
the previously determined generalizations visible to the user by
color-coding the values on the website that belong to the same column.
This is a desirable feature for our system as users will not have to
actively explore in order to discover which values are available for
scraping and how they are related to each other. On the extension and
repair front, Rousillon presents the web scraping code generated by
demonstration as an editable, high-level, block-based language called
Helena \citep{zotero-1349}. While Helena can be used to perform more
complex editing tasks like adding control flow, it does not support
adding or repairing columns after the demonstrations and presents a
change in the model used for creation. Our system maintains the model
used for creation by allowing users to extend and repair web scraping
code via demonstration.

@@

Sifter \citep{huynh2006} is a tool that augments well structured
websites with advanced sorting and filtering functionality. Like
Wildcard, it uses web scraping to extract data from websites in order to
enable customizations (sorting and filtering). Unlike Wildcard, it does
not support adding annotations to websites and running computations on
the scraped data using a spreadsheet formula language. Both of these
significantly expand the types of customizations end-users can make to
websites. Sifter performs the web scraping automatically using a variety
of heuristics and solicits guidance from the user if this fails. While
automatic web scraping seems desirable, it is unclear how useful it is
if the goal is customization. Given a row with ten scrapable values, and
therefore ten columns, would a user prefer to simply demonstrate the
value for the single column they are interested in or un-demonstrate the
nine values they are not interested in? This automatic web scraping
approach can be also be seen in tools like import.io \citep{import.io}
so it is certainly worth evaluating as part of a user study.

@@

To assess our design principles, we plan to carry out a broader
evaluation of our system through a user study. So far, we have only
tested the system amongst ourselves and a small number of colleagues.
More testing is needed to understand whether it can be successfully used
among a broader set set of users across a wider variety of websites.
Furthermore, we plan to incorporate the program viewer and
disambiguation features of FlashProg \citep{mayer2015} to give users
more insight and control into the generalization process.

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references.bib}

>>>>

Unlike text-based commands which are only valid once complete (e.g
\texttt{SELECT\ *\ FRO} versus \texttt{SELECT\ *\ FROM\ user\_table}),
the target of demonstration commands (the value of a DOM element under
the cursor) is the same during both hover and click. This allows us to
execute a command before a user completes it, thereby providing them
with a preview of the results on hover.

@@

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. Because demonstrations can span
across several websites and involve complex data access automation
tasks, its interface does not provide \emph{full} live feedback about
its generalizations or the values to be scraped until all the
demonstrations have been provided and the generated program has been
run. If run on a website it has encountered before, Rousillon makes all
the previously determined generalizations visible to the user by
color-coding the values on the website that belong to the same column.
This is a desirable feature for our system as users will not have to
actively explore in order to discover which values are available for
scraping and how they are related to each other. On the extension and
repair front, Rousillon presents the web scraping code generated by
demonstration as an editable, high-level, block-based language called
Helena \citep{zotero-1349}. While Helena can be used to perform more
complex editing tasks like adding control flow, it does not support
adding or repairing columns after the demonstrations and presents a
change in the model used for creation. Our system maintains the model
used for creation by allowing users to extend and repair web scraping
code via demonstration.

@@

Sifter \citep{huynh2006} is a tool that augments websites with advanced
sorting and filtering functionality. Similarly to Wildcard, it uses web
scraping techniques to extract data from websites in order to enable
customizations. However, Wildcard supports a broader range of
customizations beyond sorting and filtering, including adding
annotations to websites and running computations with a spreadsheet
formula language.

Our scraping tool intentionally provides less automation than Sifter.
Sifter attempts to automatically detect items and fields on the page
with a variety of clever heuristics, including automatically detecting
link tags and considering the size of elements on the page. It then
gives the user the option of correcting the result if the heuristics do
not work properly. In contrast, our heuristics are simpler and make
fewer assumptions about the structure of websites. Rather, we give more
control to the user from the beginning of the process, and incorporate
live feedback to help the user provide useful demonstrations. We
hypothesize that focusing on a tight feedback loop rather than
automation may support a scraping process that is just as fast as an
automated one, but gives the user finer control and extends to a greater
variety of websites where more complex heuristics do not apply. However,
further user testing is required to actually validate this hypothesis.

@@

To assess our design principles, we plan to carry out a broader
evaluation of our system through a user study. So far, we have only
tested the system amongst ourselves and a small number of colleagues.
More testing is needed to understand whether it can be successfully used
among a broader set of users across a wider variety of websites.
Furthermore, we plan to incorporate the program viewer and
disambiguation features of FlashProg \citep{mayer2015} to give users
more insight and control into the generalization process.

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references-bibtex.bib}
